Two Site, Single Disturbance, MultiPool

### 2021-06-14 results.Rmd

```{r, echo=FALSE,fig.cap="Simulated experiments 3-5: Left hand column shows timeseries for the wood pool for all three experiments; Right hand shows bivariate ensemble adjustment at time of disturbance"}
## figure with 3 rows, 2 col showing timeseries in rt and bivariate in left

>>>>

```{r, echo=FALSE,fig.cap="Simulated experiments 3-5: Left hand column shows timeseries for the wood pool for all three experiments; Right hand shows bivariate ensemble adjustment at time of disturbance"}

## figure with 3 rows, 2 col showing timeseries in rt and bivariate in left
